Verifying Demonstrations

### 2018-05-25 paper/DB-anon-cred.tex

We pointed out in \cref{DistanceBounding} that the majority of all \ac{DB} protocols that provide the above security properties assume an \emph{honest} verifier.
This assumption does not hold in our setting, in which every verifier might also be at some point a (malicious) prover.
We thus need public-key \ac{DB}, and more specifically \ac{DBPK}.

@@

\emph{Reattempting \iacl{DB} Schnorr protocol.}
In the original \ac{DB} paper by \citet{DistanceBounding}, they show how to 
design a distance-bounding protocol based on the Schnorr identification 
scheme~\cite{Schnorr}.
That \ac{DB} Schnorr protocol was shown to be prone to distance 
hijacking~\cite{DistanceHijacking}.
(It could not fulfil \ac{DBTF} either.)
We now propose another way to turn the Schnorr protocol into \iac{DB} protocol 
which is secure against \ac{DBMF}, \ac{DBDF}, \ac{DBDH}, \ac{DBTF} and an 
impersonating verifier (\ie it is public-key).

>>>>

@@

\emph{Reattempting \iacl{DB} Schnorr protocol.}
In the original \ac{DB} paper by \citet{DistanceBounding}, they show how to 
design a distance-bounding protocol based on the Schnorr identification 
scheme~\cite{Schnorr}.
That \ac{DB} Schnorr protocol was shown to be prone to distance 
hijacking~\cite{DistanceHijacking}.
(It was not secure against terrorist fraud either.)
We now propose another way to turn the Schnorr protocol into \iac{DB} protocol 
which is secure against \ac{DBMF}, \ac{DBDF}, \ac{DBDH}, \ac{DBTF} and an 
impersonating verifier (\ie it is public-key).

### 2018-05-25 paper/DistanceBounding.tex

The main security requirements of \ac{DB} protocols can be summarized as follows:
\begin{itemize}
  \item \ac{DBMF}: the adversary illegitimately authenticates, possibly using a 
    far-away honest prover.
  \item\ac{DBTF}: a malicious prover helps an accomplice to authenticate.
    \item \ac{DBDF}: a legitimate but malicious prover wants to fool the verifier on the distance between them.
  \item \ac{DBDH}: similar to \ac{DBDF}, sometimes using the presence of an honest prover close to the verifier.
  \item \ac{DBIF}: the adversary plays against a simplified version of the protocol without any distance estimation.
\end{itemize}
\daniel{Describe the DB frauds in more detail, \ie explain them.}
There are two lines of attempts at formalizing the above properties: one by \citet{DB-BMV} and another by \citet{DB-DFKO}.

>>>>

The main security requirements of \ac{DB} protocols can be summarized as follows:
\begin{itemize}
  \item \acf{DBMF}: the adversary illegitimately authenticates, possibly using 
    a far-away honest prover.
  \item\acf{DBTF}: a legitimate but malicious prover helps a 
    close-to-the-verifier accomplice to authenticate.
  \item \acf{DBDF}: a legitimate but malicious prover wants to fool the 
    verifier on the distance between them.
  \item \acf{DBDH}: similar to \ac{DBDF}, sometimes using the presence of an 
    honest prover close to the verifier.
  \item \acf{DBIF}: the adversary plays against a simplified version of the 
    protocol without any distance estimation.
\end{itemize}
There are two lines of attempts at formalizing the above properties: one by 
\citet{DB-BMV} and another by \citet{DB-DFKO}.
